Seismic Hazard Estimation of Northern Iran Using Smoothed Seismicity

### 2016-02-23 main.tex
start to restructure the paper.
finished first clean-up of main file

\documentclass{article}

\usepackage{textcomp}
\usepackage{amsmath}    % need for subequations
\usepackage{graphicx}   % need for figures
\usepackage{verbatim}   % useful for program listings
\usepackage{color}      % use if color is used in text
\usepackage{subfigure}  % use for side-by-side figures
\usepackage{hyperref}   % use for hypertext links, including those to external documents and URLs
\usepackage{cite}
\usepackage{float}
\usepackage{natbib}
\usepackage[utf8]{inputenc}
\usepackage{simplemargins}
\usepackage{setspace}
\usepackage{multirow}
\usepackage{url}

\usepackage{etoolbox}
\usepackage{lipsum}

\setallmargins{1in}
\onehalfspacing

\linespread{1.8} % line space

\patchcmd{\thebibliography}{\section*}{\section*}{}{}

\usepackage{xcolor}
\hypersetup{
    colorlinks,
    linkcolor={red!50!black},
    citecolor={blue!50!black},
    urlcolor={blue!80!black}
}

\title{Seismic Hazard Estimation of Northern Iran Using Smoothed Historical Seismicity}

\begin{document}

\maketitle

\newpage

\begin{center}
\textbf{Naeem Khoshnevis$^*$} \\ Graduate Research Assistant \\  University of Memphis \\ Center for Earthquake Research and Information \\   nkhshnvs@memphis.edu\\   3890 Central Ave. Memphis TN 38152 \\ Phone (901) 678-2007\\
\vspace{10 mm}
 \textbf{Shima Azizzadehroodpish}  \\ Graduate Research Assistant \\ University of Memphis \\ Center for Earthquake Research and Information \\ szzzdhrd@memphis.edu\\  
\vspace{10 mm}
\textbf{Chris H Cramer}   \\ Research  Associate  Professor \\  University of Memphis \\ Center for Earthquake Research and Information \\ ccramer@memphis.edu \\
\vspace{10 mm}
\textbf{Ricardo Taborda}   \\  Assistant  Professor \\  University of Memphis \\ Department of Civil Engineering and \\ Center for Earthquake Research and Information \\ rtbrdros@memphis.edu\\

\end{center}

\newpage

\begin{abstract}
\input{abstract}
\end{abstract}

\smallskip
\noindent \textbf{Keywords: } Seismic hazard - Spatially smoothed seismicity - Northern Iran

\input{content}

\newpage

{
\renewcommand{\bibname}{}
\bibliographystyle{ascelike}
\bibliography{PSHA}
}

\end{document}

>>>>

\RequirePackage{fix-cm}

% Document Settings
\documentclass[natbib,twocolumn]{svjour3}

% Flushing
\smartqed

% Packages
\usepackage{graphicx}
\usepackage{xcolor}
\usepackage{amsmath}
\usepackage{multirow}
\usepackage{marvosym}

% Journal Name
\journalname{Journal of Seismology}

% START: The Document
\begin{document}

% Long Title
\title{Seismic Hazard Estimation of Northern Iran Using Smoothed Seismicity}

% Running Title
\titlerunning{Seismic Hazard of Northern Iran}

% Authors
\author{%
	N.~Khoshnevis \and
	S.~Azizzadeh-Roodpish \and
	R.~Taborda \and
	C.~H.~Cramer
}

% Affiliations
\institute{%
	N.~Khoshnevis \and C.~H.~Cramer \at
	Center for Earthquake Research and Information,
	University of Memphis, 3890 Central Ave., Memphis TN 38152, USA\\
	\and
	S.~Azizzadeh-Roodpish \and R.~Taborda (\Letter)\at
	Department of Civil Engineering, and
	Center for Earthquake Research and Information,
	University of Memphis, 3890 Central Ave., Memphis TN 38152, USA\\
	\email{ricardo.taborda@memphis.edu}  
}

% Date
% \date{Received: date / Accepted: date}

% Title Production
\maketitle

% Abstract
\begin{abstract}
	\input{abstract}
	\keywords{%
		Seismic hazard \and 
		Spatially smoothed seismicity 
		\and Northern Iran
	}
\end{abstract}

% Article Content
\input{content}

% Bibliography
\bibliographystyle{spbasic}
\bibliography{PSHA}
% \nocite{*}

% END: The Document
\end{document}
